Non-kissing complexes and tau-tilting \\ for gentle algebras

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex

\begin{figure}[h]
	\capstart
	\centerline{
		\begin{tabular}{c@{\qquad}|@{\qquad}c}
			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver1}}}$ &
			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver2}}}$ \\[1.1cm]
			$I = (\alpha\beta, \gamma\delta)$ & 
			$I = (\alpha\beta, \gamma\delta, \alpha\delta)$ \\ \\ \hline \\
			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver3}}}$ &
			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver4}}}$ \\[.5cm]
			$I = (\alpha\beta, \beta\gamma, \beta^5)$ & 
			$I = (\beta\gamma)$
		\end{tabular}
	}
	\caption{Four string bound quivers. The top left and bottom right are gentle bound quivers.}
	\label{fig:exmQuiver}
\end{figure}
\end{example}

@@

\begin{example}
A gentle bound quiver~$\bar Q\ex$ and its blossoming gentle bound quiver~$\bar Q\ex\blossom$ are represented in \fref{fig:exmBlossomingQuiver}.
\end{example}

@@

\begin{example}
The $\b{g}$-vector of the plain blue walk on \fref{fig:exmFacet}\,(left) is given by $(0,-1,0,0,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$).
See \fref{fig:gcvectors} for more examples of $\b{g}$-vectors.
\end{example}

@@

\begin{example}
In the facet~$F\ex$ of \fref{fig:exmFacet}\,(right), the $\b{c}$-vector of the blue walk is~$(0,-1,0,0,0,0)$ while the $\b{c}$-vector of the yellow path is~$(0,1,0,1,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$ and \fref{fig:gcvectors}\,(left) to see the distinguished arrows in the facet~$F\ex$).
See \fref{fig:gcvectors} for more examples of $\b{c}$-vectors.

\begin{figure}[t]
	\capstart
	\centerline{$\raisebox{-1.5cm}{\begin{overpic}[scale=.6]{exmVectors}\put(60,4){$F\ex$}\end{overpic}}$ \qquad \input{gcmatrices}}
	\caption{The $\b{g}$- and $\b{c}$-matrices of the facet~$F\ex$. Their columns correspond to the $\b{g}$- and $\b{c}$-vectors of the different walks of~$F\ex$. See \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$. Note that~$\gvectors{F\ex} \cdot \cvectors{F\ex}^T = \one$.}
	\label{fig:gcvectors}
\end{figure}
\end{example}

>>>>

\begin{figure}[h]
	\capstart
	\centerline{
		\begin{tabular}{c@{\qquad}@{\qquad}c}
			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver1}}}$ &
			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver2}}}$ \\[1.1cm]
			$I = (\alpha\beta, \gamma\delta)$ & 
			$I = (\alpha\beta, \gamma\delta, \alpha\delta)$ \\ \\
			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver3}}}$ &
			$Q = \vcenter{\hbox{\includegraphics[scale=.5]{exmQuiver4}}}$ \\[.5cm]
			$I = (\alpha\beta, \beta\gamma, \beta^5)$ & 
			$I = (\beta\gamma)$
		\end{tabular}
	}
	\caption{Four string bound quivers. The top left and bottom right are gentle bound quivers.}
	\label{fig:exmQuiver}
\end{figure}
\end{example}

@@

\begin{example}
A gentle bound quiver~$\bar Q$ and its blossoming gentle bound quiver~$\bar Q\blossom$ are represented in \fref{fig:exmBlossomingQuiver}.
\end{example}

@@

\begin{example}
The $\b{g}$-vector of the plain blue walk on \fref{fig:exmFacet}\,(left) is given by $(0,-1,0,0,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q$).
See \fref{fig:gcvectors} for more examples of $\b{g}$-vectors.
\end{example}

@@

\begin{example}
In the facet~$F$ of \fref{fig:exmFacet}\,(right), the $\b{c}$-vector of the blue walk is~$(0,-1,0,0,0,0)$ while the $\b{c}$-vector of the yellow path is~$(0,1,0,1,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q$ and \fref{fig:gcvectors}\,(left) to see the distinguished arrows in the facet~$F$).
See \fref{fig:gcvectors} for more examples of $\b{c}$-vectors.

\begin{figure}[t]
	\capstart
	\centerline{$\raisebox{-1.5cm}{\begin{overpic}[scale=.6]{exmVectors}\put(60,4){$F$}\end{overpic}}$ \qquad \input{gcmatrices}}
	\caption{The $\b{g}$- and $\b{c}$-matrices of the facet~$F$ of \fref{fig:exmFacet}. Their columns correspond to the $\b{g}$- and $\b{c}$-vectors of the different walks of~$F$. See \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q$. Note that~$\gvectors{F} \cdot \cvectors{F}^T = \one$.}
	\label{fig:gcvectors}
\end{figure}
\end{example}
